Topological Equivariant Artist Model

### 2021-12-29 slides/main.tex
morphism on sheaves

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "", color=white] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& \\\& \&\\
            \opensetc_1 \subset \dbasec \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \& {}  \&                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}  \\\& \&\\
            \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf]  \& {}  \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\\& \&\\
            \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] \& {}  \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
            \end{tikzcd}
    \end{columns}
\end{frame}

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
          \dfiberc \arrow[r, hook] \& \dtotalc \arrow[d, "\pi"'] \\
           \& \dbasec \arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} \& {} \& {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\\& \&\\
            \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] \& {}  \arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf]  \& \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
            \end{tikzcd}
    \end{columns}

    \begin{description}
        \item<2-|handout:2->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<3-|handout:3>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@

    \onslide<2-|handout:2->{Given open cover $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of $\opensetc$:}
    \begin{block}<3-|handout:3->{locality}
    $\dsectionc^{1}, \dsectionc^{2} \in \sheafc(\opensetc_i)\\ \dsectionc^{1}\restriction_{\opensetc_i} = \dsectionc^{2}\restriction_{\opensetc_i} \implies \dsectionc^{1} = \dsectionc^{2}$
    \end{block} 
    \begin{block}<4-|handout:4>{gluing}
    $\dsectionc_{i} \in \sheafc(\opensetc_i), \dsectionc_{j} \in \sheafc(\opensetc_j), \opensetc_i, \opensetc_j \in \mathcal{U}\\ \dsectionc_{i}\restriction_{\opensetc_i\cap \opensetc_j} = \dsectionc_{j}\restriction_{\opensetc_i \cap \opensetc_j} \implies \dsectionc\restriction_{\opensetc_i} = \dsectionc_i$ 
    \end{block}    
\end{description}    
\end{frame}

\subsubsection{Sheaves}
\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}

>>>>

\begin{frame}{Presheaf on Bundle: $\sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}$}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<8-|handout:8->{\dfiberc}
        \onslide*<8-|handout:8->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:3->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3-|handout:3->{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} \& 
            {} \& 
            \onslide*<5-|handout:5->{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<6-|handout:6->{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<2|handout:2>{\opensetc_1 \subset \dbasec}
            \onslide*<3-|handout:3->{\opensetc_1} 
            \onslide*<4-|handout:4->{\arrow[uu, "\sheafc_{\dbasec}", color=sheaf]} 
            \onslide*<6-|handout:6->{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<7-|handout:7->{\arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf]} \& 
            \onslide*<5-|handout:5->{\opensetc_2} 
            \onslide*<5-|handout:5->{\arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{description}
        \item<8-|handout:8->[stalk]$\sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \approx \dfiberc_{\dbasepointc}$
        \item<9-|handout:9>[germ]   $\dsectionc(\dbasepointc) \in \sheafc_{\dbasec}$
    \end{description}
\end{frame}

@@

    \onslide<2-|handout:2->{Given open cover $\mathcal{\opensetc} = \{\opensetc_i\}_{i\in I}$ of $\opensetc$:}
    \begin{block}<3-|handout:3->{locality}
    $\dsectionc^{1}, \dsectionc^{2} \in \sheafc(\opensetc_i)\\ \dsectionc^{1}\restriction_{\opensetc_i} = \dsectionc^{2}\restriction_{\opensetc_i} \implies \dsectionc^{1} = \dsectionc^{2}$
    \end{block} 
    \begin{block}<4-|handout:4>{gluing}
    $\dsectionc_{i} \in \sheafc(\opensetc_i), \dsectionc_{j} \in \sheafc(\opensetc_j), \opensetc_i, \opensetc_j \in \mathcal{U}\\ \dsectionc_{i}\restriction_{\opensetc_i\cap \opensetc_j} = \dsectionc_{j}\restriction_{\opensetc_i \cap \opensetc_j} \implies \dsectionc\restriction_{\opensetc_i} = \dsectionc_i$ 
    \end{block}      
\end{frame}

\begin{frame}{Morphism on Sheaves:\onslide<5-6,8-|handout:5-6,8->{ pullback}\onslide<8-|handout:8->{ and }\onslide<7-|handout:7->{pushforward}}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-|handout:7->{\sheafc_{\gbasec}(\gbasec)} 
            \onslide*<7-|handout:7->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-|handout:7->{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbasec)}  \\
            \onslide*<2-|handout:2->{\gbasec}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-|handout:7->{\arrow[u, "\sheaf_{\gbasec}", color=sheaf]}
            \onslide*<6,8-|handout:6,8->{\arrow[d, dashed, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1->{\dbasec}
            \onslide*<4-6,8-|handout:4-6,8->{\arrow[d, "\sheaf_{\dbasec}", color=sheaf]}
            \onslide*<7-|handout:7->{\arrow[u, dashed, color=sheaf]} \\
            \onslide*<5-6,8-|handout:5-6,8->{(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec})(\gbasec)} 
            \onslide*<5-6,8-|handout:5-6,8->{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8-|handout:4-6,8->{\sheafc_{\dbasec}(\dbasec)}                             
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}
